Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-12 lab/report/include/lab2.tex
changed margins
write write

\section{Lab 2}
\label{sec:lab2}
OpenMP (Open \textbf Multi-\textbf Processing)
\todo[inline]{Introduction, one paragraph}

\subsection{Task 1}
\todo[inline]{Analyze the source code of the benchmark and provide a detailed description of how it works. Comment on the prominent communication patterns in the benchmark.}

The program reads a matrix on the form $n \times n, n \in [4,8,25,100,200]$ containing data points from a file. To make the program simpler and avoid special cases a padding is added to the matrix changing its dimensions to $(n+2) \times (n+2)$. Then every other data point, here by called red dots, is looped through. For every red dot an average of itself and its neighbors to the west, south, north, and east is calculated and written as the dots new value. For all the other data points, called black dots, the same thing is performed. The difference of the dots new and old value is added together and the process is repeated until this accumulated difference of averages is smaller than 0.01. After the program finishes its execution the matrix have converged to an average of all red and black dots.

\todo[inline]{Comment on the prominent communication patterns in the benchmark.}

@@

\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A).}}, label={lst:solve}]{include/solve.c}

\subsection{Task 3}
\todo[inline]{
Evaluate MSI, MESI, and MESI+migratory in the context of this benchmark. Perform a detailed characterization of the benchmark using different protocols. Discuss how the behavior changes when the working set size is modified. Show how execution time relates to the cache access statistics.}

>>>>

\section{Lab 2}
\label{sec:lab2}
For the second part of the lab the task is to parallelize a serial implementation of the Red-Back Gauss-Seidal algorithm. This is done using OpenMP (Open \textbf Multi-\textbf Processing) which is an API for forming multi-threaded programs in C, C++ and, Fortran. This parallel version is evaluated using the same simulator and CCP:s as in \nameref{sec:lab1}.

\subsection{Task 1}
The program reads a matrix on the form $n \times n, n \in [4,8,25,100,200]$ containing data points from a file. To make the program simpler and avoid special cases a padding is added to the matrix changing its dimensions to $(n+2) \times (n+2)$. Then every other data point, here by called red dots, is looped through. For every red dot an average of itself and its neighbors to the west, south, north, and east is calculated and written as the dots new value. For all the other data points, called black dots, the same thing is performed. The difference of the dots new and old value is added together and the process is repeated until this accumulated difference of averages, divided by $n^2$, is smaller than $0.01$. After the program finishes its execution the matrix have converged to an average of all red and black dots.

The distribution of the red and black dots forms a chess pattern. This means that when we calculate the average for a dot and its neighbors, all the neighbors are of the other color. As such, when going through for example the red dots there is no need to invalidate any other dots because the black dots are only read and you are the only one accessing your red dot.

@@

\centerline{
\begin{minipage}{1.0\textwidth}
\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A).}}, label={lst:solve}]{include/solve.c}
\end{minipage}
}
\subsection{Task 3}
\todo[inline]{
Evaluate MSI, MESI, and MESI+migratory in the context of this benchmark. Perform a detailed characterization of the benchmark using different protocols. Discuss how the behavior changes when the working set size is modified. Show how execution time relates to the cache access statistics.}
